\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-21 europa.tex
converted queen algorithm into an algorithm enviroment

A \eu user can introduce new constraint types by implementing
specialized Constraint and Propagator classes in C++, however, \eu
provides a built-in with over 25 arithmetic, temporal, set and
resource constraint types so that a large number of problem domains
can be modeled without having to introduce new constraint
types. Tables \ref{{tab:calconst, tab:setconst,
    tab:objhierarchy,tab:misc} show the constraint types.

@@

\begin{verbatim}
    public void solve(ConstraintEngine ce, int maxIter)
    {
    	curIter=0;

    	while ((ce.getViolations() > 0) && (curIter < maxIter)) {
	    Variable queenToMove = getQueenWithMaxViolation(ce);
    	     int curPos = queenToMove.getCurrentValue();

            SortedSet<int> moves = getMoves(ce,queenToMove,curPos);             
  	   boolean moved = false;
            for (int newPos : moves) {
            	moved = tryMove(queenToMove,curPos,newPos);
            	if (moved)
            	    break;
            }

            if (!moved) 
            	forceMove(queenToMove,curPos,moves.first());

            checkSolution(); // See if we have a new best solution            
            curIteration_++;
    	}
    }
\end{verbatim}

\eu's Constraint Reasoning Engine can be used to compute the non-attack constraint violations (\texttt{ce.getViolations()} is a straight call on the \eu API), 
to easily pick the queen that has he most violations by implementing \texttt{getQueenWithMaxViolation(ce)} and to look ahead and see what 
moves are possible for a queen that would remove its violations by implementing \texttt{getMoves(ce,queenToMove,curPos)}.

>>>>

A \eu user can introduce new constraint types by implementing
specialized Constraint and Propagator classes in C++, however, \eu
provides a built-in with over 25 arithmetic, temporal, set and
resource constraint types so that a large number of problem domains
can be modeled without having to introduce new constraint
types. Tables \ref{tab:calconst}, \ref{tab:setconst},
\ref{tab:objhierarchy} and \ref{tab:misc} show various constraint
types.

@@

\begin{algorithm}[H]
  \KwIn{ConstraintEngine $ce$}
  \KwIn{int $maxIter$}
  \Begin{
    $curIter \leftarrow 0$ \;
    \While{$\left( ce.getViolations() > 0 \right) ~ \& ~ \left( curIter <
        maxIter \right)$ }{
      Variable $queenToMove \leftarrow getQueenWithMaxViolation(ce)$
      \;
      SortedSet$<$int$> moves \leftarrow getMoves(ce, queenToMove,
      curPos)$ \;
      bool $moved \leftarrow $ \texttt{false} \;
      \ForEach{int $newPos$ of $moves$}{
        $moved \leftarrow tryMove(queenToMove, curPos, newPos)$\;
        \lIf{$moved$}{ \textbf{break} \; }
      }
      \lIf{$! moved$}{
        $forceMove(queenToMove, curPos, moves.first())$ \;
      }
      $checkSolution()$ \tcp*{See if we have a new best solution}
      $curIter++$ \;
    }
  }
  \caption{$solveNQueens(ce, maxIter)$}
\end{algorithm}

% \begin{verbatim}
%     public void solve(ConstraintEngine ce, int maxIter)
%     {
%     	curIter=0;

%     	while ((ce.getViolations() > 0) && (curIter < maxIter)) {
% 	    Variable queenToMove = getQueenWithMaxViolation(ce);
%     	     int curPos = queenToMove.getCurrentValue();

%             SortedSet<int> moves = getMoves(ce,queenToMove,curPos);             
%   	   boolean moved = false;
%             for (int newPos : moves) {
%             	moved = tryMove(queenToMove,curPos,newPos);
%             	if (moved)
%             	    break;
%             }

%             if (!moved) 
%             	forceMove(queenToMove,curPos,moves.first());

%             checkSolution(); // See if we have a new best solution            
%             curIteration_++;
%     	}
%     }
% \end{verbatim}

\eus Constraint Reasoning Engine can be used to compute the non-attack
constraint violations (\texttt{ce.getViolations()} is a straight call
on the \eu API), to easily pick the queen that has he most violations
by implementing \texttt{getQueenWithMaxViolation(ce)} and to look
ahead and see what moves are possible for a queen that would remove
its violations by implementing
\texttt{getMoves(ce,queenToMove,curPos)}.
